\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-18 pldi/draft.tex
Related work and conclusions

%% Author with single affiliation.
\author{
  Anonymous Author(s)\\
  \normalsize{Additional Anonymized Material: \href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.}
}
%% \authornote{with author1 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position1}
%%   \department{Department1}              %% \department is recommended
%%   \institution{Institution1}            %% \institution is required
%%   \streetaddress{Street1 Address1}
%%   \city{City1}
%%   \state{State1}
%%   \postcode{Post-Code1}
%%   \country{Country1}                    %% \country is recommended
%% }
%% \email{first1.last1@inst1.edu}          %% \email is recommended

@@

\sys's source code will be open-sourced with the camera-ready version of the paper, and is provided in anonymized form at \href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.

@@

At a high level, techniques for re-writing programs to exploit
distribution fall under a wide spectrum that ranges from fully manual
(but, ideally, optimal) to fully automated (but potentially
sub-optimal) distribution (Fig.~\ref{fig:spectrum}).  A significant
concern with approaches that require input from developers is
correctness: developers---often neither experts in distributed systems
nor educated on the internals of the code they depend on---can easily
break the semantics of centralized programs, especially when these
depend on existing code (such as libraries or shell commands).

\heading{Distributed Operating Systems and Shells}
A plethora of systems assist in the construction of distributed
software.  Distributed operating systems~\cite{ousterhout1988sprite,
  mullender1990amoeba, pike1990plan9, barak1998mosix} and programming
languages~\cite{erlang:96, acute:05, mace:07, cloudhaskell:11} hide
many distribution problems, as long as a program uses the provided
abstractions---which are strongly coupled to the underlying operating
or runtime system.
% simplify many of the problems of distribution and

Several packages expose commands for specifying parallelism on modern
\unix{}es---\eg \ttt{qsub}~\cite{gentzsch2001sun},
\textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU}
\ttt{parallel}~\cite{Tange2011a}. % or any manual
rewriting~\cite{mapreduce:08, ciel:11, spark:12}.  Different from
\sys, their effectiveness is predicated upon explicit and careful
invocation and is limited to embarrassingly parallel (and short)
programs.  Often, these commands provide options to support an array
of special sub-cases---a stark contradiction to the celebrated \unix
philosophy.  For example, \ttt{parallel} contains flags such as
\ttt{--skip-first-line}, \ttt{-trim}, and \ttt{--xargs}, that a \unix
user can achieve using \ttt{head}, \ttt{sed}, and \ttt{xargs}; it also
includes other programs with complex semantics, such as the ability
transfer files between computers, separate text files, and parse CSV.
\sys embraces the \unix philosophy and simply attempts to rewrite
pipelines more efficiently.

Several shells~\cite{duff1990rc, mcdonald1988support, dagsh:17} add
primitives for non-linear pipe topologies---some of which target
distribution.  Here too, however, developers are expected to manually
rewrite scripts to exploit these new primitives.

Recently, the Smoosh authors have argued that certain shell features
are useful for making concurrency explicit~\cite{smoosh:18}.  Their
argument is somewhat antithetical to \sys, % but rather that the shell
language is itself an good DSL for concurrency; which argues for
automatically (and correcctly) parallelizing pipelines when users have
not expressed parallelism explicitly---hence
distribution-\emph{oblivious} shell scripting.

\heading{Cluster Computing}
Modern analytics frameworks~\cite{mapreduce:08, ciel:11, spark:12,
  naiad:13} and domain-specific languages~\cite{alvaro2011consistency,
  distal:13, meiklejohn2015lasp} go a step further in terms of
automation by providing a few carefully-designed primitives.  These
primitives make strong assumptions about the nature of the
computation---\eg strongly-eventual commutative functions that can
proceed in parallel.  By targeting specific classes of computation
(\emph{viz.} \sys's parallelizability), they render distributed
computation efficiently.

% Lack of generality, no formal guaratees, their setup and is too tedious 
\sys chooses a more general approach: it does not require users to set
up a new framework for every new class of computation they need to
execute, nor to rewrite different parts of their computation using the
specific abstractions provided by each framework they use.  It also
takes a more principled approach: by developing the semantic model
outlined earlier, it can guarantee that transformations are correct
with respect to the sequential program.

@@

\heading{Annotation-based Distribution}
Recent systems on light-touch distribution, such as
Ignis~\cite{ignis:19} and Mozart~\cite{mozart:19}, are more general
than cluster-computing frameworks.  They also lower (but not entirely
eliminate) developer effort by automating most of the rewriting
process.
% Both work on high-level, managed languages---server-side JavaScript for Ignis and Python for Mozart---that allow runtime transformations without affecting the broader environment under which a program executes.
For the critical points where user input is required, they provide a
high-level declarative DSL with varying (but limited) degrees of
expressive power.
% Annotations are used by ---complicated by the use of third-party
% libraries similar to \sys's extensions.
Unfortunately, a challenge with this approach is that users composing
applications by using third-party libraries do not understand their
parallelizability details well-enough to annotate them.

\sys occupies a different point in the design space, by removing any work from composers and adding a small load to developers.
% More specifically, it is designed to be used automatically by composers,
Its DSL is designed to be more heavy-weight than Ignis' declarative recipes or Mozart's split annotations, but geared towards the developers of these components---not the users composing them.

@@

% Nice intro: http://homepages.inf.ed.ac.uk/bfranke/Publications/pldi121-tournavitis.pdf
\heading{Low-level Parallelization}
Instruction-level parallelization has a longer history, starting from
explicit \ttt{DOALL} and \ttt{DOACROSS} annotations~\cite{par1, par2}
and continuing with compilers that attempt to automatically extract
parallelism~\cite{padua1993polaris,hall1996maximizing}.  These systems
operate at a lower level than \sys (\eg that of instructions or loops
instead of pipe boundaries) and typically do not exploit runtime
information.

More recent work focuses on extracting parallelism from
domain-specific programming models~\cite{cilk5, streamIt, galois} and
interactive parallelization tools~\cite{parascope, ipat}.  These tools
simplify the expression of parallelism, but still require programmers
to get involved in discovering and exposing parallelism.
%  actively involve the programmer in the detection and mapping of application parallelism, but still demand great effort from the user. 
Moreover, the insights behind these attempts are significantly different from ours, as they extract parallelism statically during compilation instead of dynamically during runtime.
%Despite significant progress~\cite{}, it remains due to its need for complex program analysis and the unknown factors (such as input data range) during compilation.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_spectrum.pdf}}
\caption{
  \textbf{Manual--automated distribution spectrum.}
	\sys sits at the automation end of the spectrum, automatically distributing shell pipelines while maintaining their correctness.
}
\vspace{-15pt}
\label{fig:spectrum}
\end{figure}

@@

\heading{Correct Distribution of Dataflow Graphs}
%
The dataflow graph is a prevalent model in several areas of data
processing, as it is used by several batch-~\cite{mapreduce:08,
  spark:12} and stream-processing systems~\cite{murray2013naiad,
  carbone2015flink}. Despite its popularity, most systems perform
optimizations that do not preserve its semantics, introducing subtle
erroneous behaviours. Recent work~\cite{HSSGG2014, SHGW2015,
  MSAIT2019} attempts to address this issue by performing
optimizations only in cases where correctness is preserved. \sys draws
inspiration from these efforts, as we are also interested in
optimizations that exploit parallelization but preserve the semantics
of the underlying model. However, our proposed dataflow model is
different from these other works, as nodes in our model read from
their inputs \emph{in sequence}. Due to this intricacy, previous work
is not straightforwardly applicable.

@@

\section{Discussion}
\label{discussion}

This section reflects on \sys's design and implementation, touches on future work, and concludes the paper.

\heading{Limitations}
Our implementation is limited in many ways, so as to succeed in proving the key hypothesis---that scaling out shell pipelines can be automated and correct with respect to some assumptions.

\sys does not adequately handle failures or network partitions in the general sense, which would require re-scheduling passes on failed replicas.
Prior work on fault-tolerant distributed stream processing can be of significant aid here.

The logic of the planner is quite simplified, attempting only straightforward placement of tasks to nodes (and using a hard-coded, homogeneous node structure).
Prior work on operator placement of distributed dataflow graphs can be used to build a more sophisticated planner.

\sys is conservative in the shell subsets that it handles, in order to
avoid introducing unsafe behaviours. The point of this work was not to be
able to handle a complete distributable subset of the shell, but
rather to use significant part of it to demonstrate performance benefits.

% Shell is highly dynamic, thus making it impossible to design sound
% meaningful analyses to determine distributable regions and maximal
% parallelization. In order to address this particularity, \sys could be
% tighly integrated with a posix compliant shell
% interpreter~\cite{smoosh:20} so that dynamic information can be
% acquired selectively to aid the analysis and optimization process.

\heading{Future Work}
% \label{limitation}
% \item No cycles (multiple commands writing and reading from the same file)
There are several worthwhile directions for future work.  One
direction would be an extension of the parallelizability analysis of
\sys, in order to guide it using dynamic information. This could
enable a formal study of the analysis~\sx{impl} to show that it
returns regions that are safe to distribute.  Recent work on
formalizing the semantics of the POSIX shell~\cite{smoosh:20} make
such an attempt possible.

Another direction is to extend \sys to handle other classes outside \sta and \pur.
These two classes enjoy a certain popularity with quick, one-off pipelines and are the easiest to distribute, but 
it would be interesting to expand to \dfs (with the use of a distributed file-system) and \sid (with the use of transactional protocols).
This direction would naturally introduce considerations about replication, consistency, and failure recovery.

% There are two additional assumptions that have to be satisfied in
% order for the distributed implementation that is generated by Dish to
% have equivalent behaviour with the original implementation. First of
% all, there should be no external signals to the commands while they
% execute. At the moment Dish assumes no faults, and that communication
% always succeeds. This assumption can be lifted by extending Dish with
% a fault-tolerant runtime, \kk{blah blah}. Second, we assume that no
% command reads and writes to arbitrary files that are not mentioned in
% their arguments. This is a necessary assumption, since commands are
% considered as black boxes and the only information that can be
% inferred about them is through their arguments.

\heading{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express streaming computations that can be automatically distributed.
To achieve its goal, \sys
  decomposes primitives into parallelizability classes,
  identifies high-parallelizability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.

@@

@@

\newpage

% \begin{figure}
%   \centering
%   \begin{grammar}
%     <option> ::= `-' <string>
% 
%     <category> ::= `stateless' | `pure' | ...
% 
%     <maybe-int> ::= | <int>
% 
%     <arg> ::= `args[' <int> `]'
% 
%     <args> ::= <arg>
%     \alt `args[' <maybe-int> `:' <maybe-int> `]'
% 
%     <input> ::= `stdin' | <args>
% 
%     <inputs> ::= <input>
%     \alt <input> `,' <inputs>
% 
%     <output> ::= `stdout' | <arg>
% 
%     <option-pred> ::= <option>
%     \alt `value' <option> = <string>
%     \alt `not' <option-pred>
%     \alt <option-pred> `or' <option-pred>
%     \alt <option-pred> `and' <option-pred>
% 
%     <assignment> ::= `(' <category>, `[' <inputs> `]' , <output> `)'
% 
%     <predicate> ::= <option-pred> `=>' <assignment>
% 
%     <pred-list> ::= `|' <predicate> <pred-list>
%     \alt `|' `otherwise' `=>' <assignment>
% 
%     <command> ::= <name> `\{' <pred-list> `\}'
% 
%     <command-list> ::= <command>
%     \alt <command> <command-list>
%   \end{grammar}
%   \caption{
%   \textbf{Parallelizability description language.}
%     The DSL captures important information regarding the parallelizability of a command.
%   }
%   \label{fig:dsl}
% \end{figure}

>>>>

%% Author with single affiliation.
\author{
  Anonymous Author(s)\\
  \normalsize{Additional Anonymized Material: \href{https://git.io/JfEgr}{https://git.io/JfEgr}.}
}
%% \authornote{with author1 note}          %% \authornote is optional;
%%                                         %% can be repeated if necessary
%% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%% \affiliation{
%%   \position{Position1}
%%   \department{Department1}              %% \department is recommended
%%   \institution{Institution1}            %% \institution is required
%%   \streetaddress{Street1 Address1}
%%   \city{City1}
%%   \state{State1}
%%   \postcode{Post-Code1}
%%   \country{Country1}                    %% \country is recommended
%% }
%% \email{first1.last1@inst1.edu}          %% \email is recommended

@@

\sys's source code will be open-sourced with the camera-ready version of the paper, and is provided in anonymized form at \href{https://git.io/JfEgr}{https://git.io/JfEgr}.

@@

At a high level, techniques for re-writing programs to exploit parallelism fall under a wide spectrum that ranges from fully manual (but, ideally, optimal or more general) to fully automated (but potentially sub-optimal or specialized).
A significant concern with approaches that require user input is correctness:
   users---often neither experts in parallelism nor educated on the internals of the code they depend on---can easily break the semantics of sequential programs, especially when these depend on existing code (such as is the case with shell commands).

\heading{Parallel Shell Scripting}
Several utilities expose commands for specifying parallelism on modern \unix{}es---\eg \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}.
Different from \sys, their effectiveness is predicated upon explicit and careful invocation and is limited to embarrassingly parallel (and short) programs.
Often, these commands provide options to support an array of special sub-cases---a stark contradiction to the celebrated \unix philosophy.
For example, \ttt{parallel} contains flags such as \ttt{--skip-first-line}, \ttt{-trim}, and \ttt{--xargs}, that a \unix user can achieve using \ttt{head}, \ttt{sed}, and \ttt{xargs};
   it also introduces (and depends on) other programs with complex semantics, such as the ability transfer files between computers, separate text files, and parse CSV.
\sys embraces the \unix philosophy and simply attempts to rewrite pipelines more efficiently with minimal user effort---if any.

Several shells~\cite{duff1990rc, mcdonald1988support, dagsh:17} add primitives for non-linear pipe topologies---some of which target parallelism.
Here too, however, users are expected to manually rewrite scripts to exploit these new primitives, contrary to \sys.

Recently, the Smoosh authors have argued that certain shell features are useful for making concurrency explicit~\cite{smoosh:18}.
Their argument is somewhat antithetical to \sys, which argues that users should experience mostly automated (and correct) parallelization---hence \emph{light-touch} parallel scripting.

% Nice intro: http://homepages.inf.ed.ac.uk/bfranke/Publications/pldi121-tournavitis.pdf
\heading{Low-level Parallelization}
Instruction-level parallelization has a long history, starting from explicit \ttt{DOALL} and \ttt{DOACROSS} annotations~\cite{par1, par2} and continuing with compilers that attempt to automatically extract parallelism~\cite{padua1993polaris,hall1996maximizing}.
These systems operate at a lower level than \sys (\eg that of instructions or loops rather than the boundaries of programs that are part of a script), operating in a single target environment, and typically do not exploit high-level annotations.

More recent work focuses on extracting parallelism from domain-specific programming models~\cite{cilk5, streamIt, galois} and interactive parallelization tools~\cite{parascope, ipat}.
These tools simplify the expression of parallelism, but still require users to get involved in discovering and exposing parallelism.
% Moreover, the insights behind these attempts are significantly different from \sys's, as they extract parallelism statically during compilation instead of dynamically during runtime.
%Despite significant progress~\cite{}, it remains due to its need for complex program analysis and the unknown factors (such as input data range) during compilation.

\heading{Correct Parallelization of Dataflow Graphs}
The DFG is a prevalent model in several areas of data processing (including batch-~\cite{mapreduce:08, spark:12} and stream-processing ~\cite{murray2013naiad, carbone2015flink} systems).
Despite its popularity, most systems perform optimizations that do not preserve its semantics, introducing subtle erroneous behaviours.
Recent work~\cite{HSSGG2014, SHGW2015, MSAIT2019} attempts to address this issue by performing optimizations only in cases where correctness is preserved.
\sys draws inspiration from these efforts, as it attempts transformations that maintain the program's correctness with respect to the sequential execution.

\sys's proposed DFG model is diverges from prior works, as nodes it captures order.
This is due to the intricacies of the \unix model---its streams, its argument processing, and concatenation operators all maintain ordering.
% As a result, previous work is not directly applicable.

\heading{Parallel Userspace Environments}
By focusing on simplifying the development of distributed programs, a plethora of environments assist in the construction of parallel software.
Such systems~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} or languages~\cite{erlang:96, acute:05, mace:07, cloudhaskell:11} hide many of the challenges of dealing with concurrency.
They do so as long as a program leverages the provided abstractions---which are strongly coupled to the underlying operating or runtime system.
A notable example is Plan9's \ttt{rc} shell that provided an interface for the construction of general programs.
Unfortunately these environments are not backward-compatible with the \unix shell, and often focus primarily on hiding the existence of a network---providing the illusion of a single-system image---rather than automatically accelerating scripts through parallel processing.
% simplify many of the problems of distribution and

\heading{Cluster Computing}
Several frameworks such as Phoenix~\cite{} and Raftlib~\cite{} offer full automation as long as their use leverages special primitives---\eg map-reduce-style primitives for Phoenix.
These primitives make strong assumptions about the nature of the computation---\eg strongly-eventual commutative functions that can proceed in parallel.
By targeting specific classes of computation (\emph{viz.} \sys's parallelizability), they can significantly optimize for their target domains.

% Lack of generality, no formal guaratees, their setup and is too tedious 
\sys chooses a more general approach: it does not require users to set up a new framework for every new class of computation they need to execute, nor to rewrite different parts of their computation using the specific abstractions provided by each framework they use.
It also takes a more principled approach: by developing the semantic model outlined earlier, it can focus on transformations that are correct with respect to the sequential program.

@@

% \heading{Annotation-based Transformations}
% \sys inspiration from recent systems such as Ignis~\cite{ignis:19} and Mozart~\cite{mozart:19} which, as long as a developer has provided a few high-level annotations, they take care of automating scale-out.
% % Both work on high-level, managed languages---server-side JavaScript for Ignis and Python for Mozart---that allow runtime transformations without affecting the broader environment under which a program executes.
% These systems works on single-language, single-runtime environments 
% 
% For the critical points where user input is required, they provide a
% high-level declarative DSL with varying (but limited) degrees of
% expressive power.
% % Annotations are used by ---complicated by the use of third-party
% % libraries similar to \sys's extensions.
% Unfortunately, a challenge with this approach is that users composing
% applications by using third-party libraries do not understand their
% parallelizability details well-enough to annotate them.
% 
% \sys occupies a different point in the design space, by removing any work from composers and adding a small load to developers.
% % More specifically, it is designed to be used automatically by composers,
% Its DSL is designed to be more heavy-weight than Ignis' declarative recipes or Mozart's split annotations, but geared towards the developers of these components---not the users composing them.

@@

@@

% \begin{figure}[t]
% \centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_spectrum.pdf}}
% \caption{
%   \textbf{Manual--automated distribution spectrum.}
% 	\sys sits at the automation end of the spectrum, automatically distributing shell pipelines while maintaining their correctness.
% }
% \vspace{-15pt}
% \label{fig:spectrum}
% \end{figure}
%

@@

@@

\section{Discussion \& Conclusion}
\label{discussion}

This paper presented \sys, a shell variant that parallelizes shell programs mostly automatically.
\sys's insight is that shell pipelines already express streaming computations that can be automatically distributed.
To achieve its goal, \sys
  decomposes primitives into parallelizability classes,
  identifies high-parallelizability stages,
  applies a series of transformations according to a DFG model,
  and orchestrates the execution of the parallel program.
% Its runtime component provides orchestration and planning support during the execution of the program.

\sys's current limitations revolve around shell expansion.
Currently, \sys does not attempt to parallelize program fragments for which variables have not been expanded.
Without substantial effort, \sys could be modified to at least suggest expansion of these fragments so that developers provide concrete values.
More significant effort would be required however to fully exploit latent parallelism in fragments that have not been expanding.
This effort would require tying \sys with the shell interpretation rather than having it as a compilation pass and is left for future work.

Despite limitation related to expansions, \sys can lead to significant benefits for shell users.
Experiments with real programs show substantial speedups and the ability to operate on large input datasets, all minimal or zero developer effort.

% \heading{Limitations}
% Our implementation is limited in many ways, so as to succeed in proving the key hypothesis---that scaling out shell pipelines can be automated and correct with respect to some assumptions.
% 
% \sys does not adequately handle failures or network partitions in the general sense, which would require re-scheduling passes on failed replicas.
% Prior work on fault-tolerant distributed stream processing can be of significant aid here.
% 
% The logic of the planner is quite simplified, attempting only straightforward placement of tasks to nodes (and using a hard-coded, homogeneous node structure).
% Prior work on operator placement of distributed dataflow graphs can be used to build a more sophisticated planner.
% 
% \sys is conservative in the shell subsets that it handles, in order to
% avoid introducing unsafe behaviours. The point of this work was not to be
% able to handle a complete distributable subset of the shell, but
% rather to use significant part of it to demonstrate performance benefits.
% 
% % Shell is highly dynamic, thus making it impossible to design sound
% % meaningful analyses to determine distributable regions and maximal
% % parallelization. In order to address this particularity, \sys could be
% % tighly integrated with a posix compliant shell
% % interpreter~\cite{smoosh:20} so that dynamic information can be
% % acquired selectively to aid the analysis and optimization process.
% 
% 
% \heading{Future Work}
% % \label{limitation}
% % \item No cycles (multiple commands writing and reading from the same file)
% There are several worthwhile directions for future work.  One
% direction would be an extension of the parallelizability analysis of
% \sys, in order to guide it using dynamic information. This could
% enable a formal study of the analysis~\sx{impl} to show that it
% returns regions that are safe to distribute.  Recent work on
% formalizing the semantics of the POSIX shell~\cite{smoosh:20} make
% such an attempt possible.
% 
% Another direction is to extend \sys to handle other classes outside \sta and \pur.
% These two classes enjoy a certain popularity with quick, one-off pipelines and are the easiest to distribute, but 
% it would be interesting to expand to \dfs (with the use of a distributed file-system) and \sid (with the use of transactional protocols).
% This direction would naturally introduce considerations about replication, consistency, and failure recovery.
% 
% There are two additional assumptions that have to be satisfied in
% order for the distributed implementation that is generated by Dish to
% have equivalent behaviour with the original implementation. First of
% all, there should be no external signals to the commands while they
% execute. At the moment Dish assumes no faults, and that communication
% always succeeds. This assumption can be lifted by extending Dish with
% a fault-tolerant runtime, \kk{blah blah}. Second, we assume that no
% command reads and writes to arbitrary files that are not mentioned in
% their arguments. This is a necessary assumption, since commands are
% considered as black boxes and the only information that can be
% inferred about them is through their arguments.

@@

\begin{figure}
  \centering
  \begin{grammar}
    <option> ::= `-' <string>

    <category> ::= `stateless' | `pure' | ...

    <maybe-int> ::= | <int>

    <arg> ::= `args[' <int> `]'

    <args> ::= <arg>
    \alt `args[' <maybe-int> `:' <maybe-int> `]'

    <input> ::= `stdin' | <args>

    <inputs> ::= <input>
    \alt <input> `,' <inputs>

    <output> ::= `stdout' | <arg>

    <option-pred> ::= <option>
    \alt `value' <option> = <string>
    \alt `not' <option-pred>
    \alt <option-pred> `or' <option-pred>
    \alt <option-pred> `and' <option-pred>

    <assignment> ::= `(' <category>, `[' <inputs> `]' , <output> `)'

    <predicate> ::= <option-pred> `=>' <assignment>

    <pred-list> ::= `|' <predicate> <pred-list>
    \alt `|' `otherwise' `=>' <assignment>

    <command> ::= <name> `\{' <pred-list> `\}'

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
  \textbf{Parallelizability description language.}
    The DSL captures important information regarding the parallelizability of a command.
  }
  \label{fig:dsl}
\end{figure}

@@
